Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-07-02 ms.tex
Adding xinit plot for tau=1e6

Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $\sigma_s$ away from line center, their agreement with Monte Carlo as a function of source frequency can also be characterized. Photons initialized closer to the line wing may travel larger mean free paths as the opacity is sensitively dependent on the line profile. The larger spatial diffusion contributes to greater escape probability, biasing the frequency distribution of escaping photons. In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function in frequency as all photons escape the gas without scattering. Fig. \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$. The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core. On this point, we note that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases. Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows. %Note: should we characterize this scaling quantitatively?

>>>>

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel_tau1e6.pdf}
    \caption{Again shifting the initial photon frequency, but at a lower optical depth of $\tau_0 = 10^6$. The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic. } 
    \label{fig:sol_mc_xinit_lowtau}
\end{figure}

Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $\sigma_s$ away from line center, their agreement with Monte Carlo as a function of source frequency can also be characterized. Photons initialized closer to the line wing may travel larger mean free paths as the opacity is sensitively dependent on the line profile. The larger spatial diffusion contributes to greater escape probability, biasing the frequency distribution of escaping photons. In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function in frequency as all photons escape the gas without scattering. Fig. \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$. The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core. On this point, we note that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases. Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows. The bias in the escaping spectrum is much more noticeable at lower optical depths, shown in Fig. \ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a significantly larger fraction of the spectral peak location $(a\tau_0)^{1/3}$. Here it is more clear that as the photon initialization frequency becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
